Meta RL analyses

### 2018-10-18 meta_RL_analyses.Rmd
Some refactoring, and meta_true basic analysis

```{r}
num_runs = 3
results_dir = "results/results_smd/"

new_game_strs = c("game_straight_flush_l_1_bv_1_sr_0")
```

```{r}
reward_d = data.frame()
for (run_i in 0:(num_runs-1)) {
  filename = sprintf("%srun%i_%s.csv", results_dir, run_i, "new_rewards")
  if (!file.exists(filename)) {
    next
  }
  this_d = read.csv(filename, header=T) %>%
    mutate(run = run_i)
  reward_d = bind_rows(reward_d, this_d)
}

@@

>>>>

```{r}
num_runs = 1
results_dir = "results/results_no_hints_2/"

new_game_strs = c("game_straight_flush_l_1_bv_0_sr_0",
                  "game_straight_flush_l_1_bv_1_sr_0",
                  "game_straight_flush_l_1_bv_0_sr_1",
                  "game_straight_flush_l_1_bv_1_sr_1")
```

# utils

```{r}
load_d = function(results_dir, num_runs, file_type) {
  d = data.frame()
  for (run_i in 0:(num_runs-1)) {
    filename = sprintf("%srun%i_%s.csv", results_dir, run_i, file_type)
    if (!file.exists(filename)) {
      next
    }
    this_d = read.csv(filename, header=T) %>%
      mutate(run = run_i)
    d = bind_rows(d, this_d)
  }
  return(d)
}
```

# meta-learning tests

```{r}
reward_d = load_d(results_dir, num_runs, "new_rewards")

@@

# meta mapping (true) evaluation

```{r}
meta_d = load_d(results_dir, num_runs, "new_meta_true_losses")

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  gather(map_str, reward, -c(run, epoch)) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = source %in% new_game_strs | target %in% new_game_strs)
```

```{r}
avg_meta_d = meta_d %>%
  group_by(run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward)) %>%

```

```{r}
ggplot(avg_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
# geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2")
```
